% Autogenerated translation of _readme.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\chapter*{tpf-tools-intermediate}

‘tpf-tools-intermediate’ is a bundle of tools for low-latency, bidirectional, multichannel transmission of audio and video. 
Version 1.1.1 is compatible with macOS 10.14+ (only Intel).

\hrule
\subsection*{Important}

\begin{itemize}
\item Make sure that you have installed jack2 for osx!
\item Make sure that you have created an 'aggregate - device' in the ‘Audio MIDI Setup !
\end{itemize}

\section*{Download:}

\begin{itemize}
\item Go to GitHub: \href{https://github.com/zhdk/tpf-installers/releases}{https://github.com/zhdk/tpf-installers/releases}
\item Download the 'install-tpf-tools-intermediate.pkg'
\end{itemize}

\section*{Installation:}

\begin{itemize}
\item Right-click to open the 'install-tpf-tools-intermediate.pkg' and follow the instructions of the installer.
\item Right-click to open the "tpf-audio-runner.command" file, and follow the messages of the "tpf-audio-runner.command" script.
\end{itemize}

More information and instructions can be found at:\href{https://networkperformance.space}{https://networkperformance.space}

\hrule
\section*{Content of tpf-tools-intermediate:}

\subsection*{Applications:}

\begin{itemize}
\item tpf-party (v1.1.1)
\item tpf-client (v1.1.1)
\item Ardour6.8
\item uv-qt (Ultragrid 1.6)
\end{itemize}

\subsection*{Scripts:}

\begin{itemize}
\item tpf-audio-runner.command
\item tpf-video-runner.command
\end{itemize}

\subsection*{Folders:}

\textbf{tpf-settings:}

\begin{itemize}
\item tpf-intermediate-2ch-2loc
\item tpf-intermediate-4ch-4loc
\item tpf-intermediate-default
\end{itemize}

\textbf{ardour-templates:}

\begin{itemize}
\item tpf-intermediate-2ch-2loc.ardour
\item tpf-intermediate-4ch-4loc.ardour
\item tpf-intermediate-default.ardour
\item tpf-start.ardour
\end{itemize}

\textbf{tpf-video:}

\begin{itemize}
\item camera-0.command
\item camera-1.command
\item camera-2.command
\item selftest-camera-0.command
\item selftest-camera-1.command
\item selftest-camera-2.command
\item tpf-video-runner.command
\end{itemize}

\textbf{tpf-uninstallers:}

\begin{itemize}
\item uninstall-tpf-jack2.command
\item uninstall-tpf-tools-intermediate.command
\end{itemize}

\hrule
\section*{Start the tpf-tools-intermediate:}

\begin{itemize}
\item After installation, start your session:
\item \textbf{Audio}: double-click the file ‘tpf-audio-runner.command’ 
\item Follow the instructions in the terminal window.
\item \textbf{Video}: double-click the file ‘tpf-video-runner.command’ from the ‘tpf-video’-folder. 
\item Follow the instructions in the terminal window.
\end{itemize}

\hrule
\subsection*{About Applications}

\textbf{Ardour 6.8}

\href{https://ardour.org/}{https://ardour.org/}

\textbf{Ultragrid}

\href{http://www.ultragrid.cz/}{http://www.ultragrid.cz/} 

\textbf{TPF-Client}

\href{https://github.com/zhdk/tpf-client}{https://github.com/zhdk/tpf-client}

\href{https://networkperformance.space}{https://networkperformance.space} (including manuals)

\textbf{LoudMax} (VST/VST3/AU)

Loudness Maximizer plugin by Thomas Mundt.

\href{https://loudmax.blogspot.com}{https://loudmax.blogspot.com} for updates.

\hrule
\subsection*{Authors:}

\begin{itemize}
\item Roman Haefeli \href{mailto:roman.haefeli@zhdk.ch}{roman.haefeli@zhdk.ch}
\item Johannes Schütt \href{mailto:johannes.schuett@zhdk.ch}{johannes.schuett@zhdk.ch}
\item TPF-Team @ Zurich University of the Arts (ZHdK)
\end{itemize}

\hrule
\subsection*{License}

GPL 3.0 (view LICENSE.txt)

\hrule
\end{document}
